### 2021-10-26 SujetStage/2021-pNetsubjectM2.tex
version v1

In the previous years, we have studied theoretical foundations for open
systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
automata are much more complex than transitions of an LTS as the ﬁring on a transition depends on parameters and actions that are symbolic.

Establishing  whether two open automata are composable or not require the designer to provide the behaviour of all holes in a context where they are used; which consists in describing all the interactions and the series of inputs and outputs of data exchanged  between the automata.  To make this task reusable by other designers, we are interested in characterising  the behavioural condition that must be satisfied by a process that would be plugged into a hole to satisfy the composability condition.

To tackle this issue, we ask: Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton whose hole is compatible with this global type?

@@

The main objective of the internship  deals with the characterization of dynamic execution of open automata as behavioural types. Our purpose is to define the composability condition of two open automata.

The internship will start with a study of the semantics of  open automata and the notion behavioural types \cite{Hans:2016}, in particular the notion of session types that allows to describe the dynamic aspects of processes.

>>>>

In the previous years, we have studied theoretical foundations for open
systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic.

Establishing  whether two open automata are equivalent  or not requires the designer to provide the behaviour of all holes in a context where they are used; which consists in describing all the interactions and the series of inputs and outputs of data exchanged  between the automata and its environment.  
To make those reusable, we are interested in enriching holes with description of behaviours to give them enough power and enable us to check equivalences for these open systems. The description will characterise the assumptions that the automaton makes about the behavior of its surroundings  in order to guarantee certain conditions.

To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton  with compatible  surrounding automaton? }

@@

The main objective of the intern ship  deals with the characterization of interactions  of open automaton with its environment as behavioural types.
More specifically, the intern ship would follow the following steps:
\begin{itemize}
\item The internship will start with a familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016}, in particular the notion of session types that allows to describe the dynamic aspects of processes.

\item Design of an adequate characterisation of  compatibility condition  suitable for the composition open automata, and which is sufficient to decide if two open automata are compatible or not. 
\item Examples/Algorithm

\end{itemize}
